### 2019-05-09 2-Chapters/6-Chapter/nonstatbandits.git/NonStatB.tex
Trying to fix last issue on Chapter6

@@

>>>>

\begin{figure}[h!]  % [htbp]
    \centering
    \includegraphics[width=1.00\linewidth]{2-Chapters/6-Chapter/Images/Visualizing_locations_of_change_points_for_different_algorithms__4algs_Pb1.pdf}
    \caption{Location of the detected change-points for four algorithms on Problem 1.}
    \label{fig:6:Visualizing_locations_of_change_points_for_different_algorithms__4algs_Pb1}
\end{figure}

@@

\begin{figure}[h!]  % [htbp]
    \centering
    \includegraphics[width=1.00\linewidth]{2-Chapters/6-Chapter/Images/Visualizing_locations_of_change_points_for_different_algorithms__4algs_Pb2.pdf}
    \caption{Location of the detected change-points for four algorithms on Problem 2.}
    \label{fig:6:Visualizing_locations_of_change_points_for_different_algorithms__4algs_Pb2}
\end{figure}
